\documentclass[landscape]{article}
\setlength{\headheight}{15pt}
\usepackage[margin=2cm]{geometry} 
\usepackage{nopageno}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Science or Superstitition}
\chead{Spring 2020}
\rhead{Fallacies Cheat Sheet}
\lfoot{}
\cfoot{}
\rfoot{}

\newcommand{\wide}{\setlength{\parskip}{12mm}}
\newcommand{\notsowide}{\setlength{\parskip}{5mm}}
\begin{document}


\subsubsection*{Fallacies of Relevance}
\begin{enumerate}%\notsowide
\item \textbf{Appeal to Authority}: Some authority figure concludes that $X$ is true, wrong, etc. Thus $X$ is true, wrong, etc.

\item \textbf{Ad Hominem} (personal attack): Person $Y$ claims $X$ is true. But person $Y$ is a an awful person, a hypocrite, or smells bad. Thus person $Y$'s argument for $X$ can be dismissed.

\item \textbf{Popular Appeal}: Many people endorse $X$, thus $X$ is true, good, etc.

\item \textbf{Appeal to Force}: Believe $X$ or you die!

\item \textbf{Appeal to Consequences}: Theory $X$ has bad consequences, thus theory $X$ is false.

\item \textbf{Naturalistic Fallacy}: $X$ is natural, thus $X$ is good.

\item \textbf{Genetic Fallacy}: $X$ comes from $y$, thus $X$ has all of the features of $y$.

\item \textbf{Red Herring}: You say $X$ is true, good, etc. What about $Y$?

\item \textbf{Weak Analogy}: $X$ has feature $F$. $Y$ is almost, sort of like $X$, so $Y$ has feature $F$. 
\end{enumerate}
\subsubsection*{Fallacies of Ambiguity}
\begin{enumerate} %\notsowide
\item \textbf{Equivocation}: One meaning of a word, implies another meaning of the same word.

\item \textbf{Straw Person}: Your argument can be refuted by refuting this much weaker version of it.

\item \textbf{Cherry Picking (Texas Sharpshooter}: These particular data points support $X$, so $X$ is true.


\end{enumerate}

\subsubsection*{Fallacies of Presumption}

\begin{enumerate} %\notsowide

\item \textbf{Mere Assertion}: $X$ is true!

\item \textbf{Begging the Question}: $X$ is true, because $X$ is true.

\item \textbf{Appeal to Ignorance}: We are not sure if $X$ is true. So $X$ is false.

\item \textbf{False Dilemma}: Either you accept $X$ or you must accept as the only alternative, awful position $Y$.

\item \textbf{Hasty Generalization}: A small, biased sample shows that $X$ is true.

\item \textbf{Slippery Slope}: If we do innocent-sounding $X$, awful consequence $Y$ will also happen.

\item \textbf{False Cause}: $X$ happened before $Y$, so $X$ caused $Y$.

\item \textbf{Circular Reasoning}: $X$ proves $Y$, and $Y$ proves $X$.
\end{enumerate}





\end{document}
