\documentclass[]{article}
\setlength{\headheight}{15pt}
\usepackage[margin=2cm]{geometry} 
\usepackage{nopageno}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Science or Superstitition}
\chead{Spring 2020}
\rhead{Fallacies}
\lfoot{}
\cfoot{}
\rfoot{}

\newcommand{\wide}{\setlength{\parskip}{12mm}}
\newcommand{\notsowide}{\setlength{\parskip}{5mm}}
\begin{document}

\textbf{Identify the fallacy.}

\begin{enumerate}\wide
\item We shouldn't ban the carrying of concealed weapons in public places because the next thing you know we'll be banning hunting rifles too.

\item You can't prove that there isn't a God. Therefore God must exist.

\item I saw a bunch of drunk Buddhists beating up an old man the other day. I had no idea that Buddhism encouraged such behavior, but I guess it does.

\item A study funded by Monsanto corporation claims to show that the weed killer Roundup, which they manufacture, is not toxic to humans. That study can obviously be dismissed as propaganda.

\item A few prominent engineers believe that 9-11 was the result of a conspiracy, therefore there is a good reason to suspect that it was.

\item Getting rid of privacy and putting in place universal electronic surveillance is only a bad idea if you have something to hide. Since you oppose such surveillance, you clearly have something to hide.

\item Diagnoses of brain cancer went up shortly after "The Simpsons" first went on TV. Thus watching the Simpsons must cause brain cancer.

\item Eating dogs is wrong. Why? Because nobody I know does it!

\item Ghosts are real, I've seen them with my own eyes!

\item I refuse to take pills produced by pharmaceutical companies in their chemical plants! It is much better to take only all-natural herbal extracts.

\end{enumerate}

\pagebreak


\subsubsection*{Fallacies of Relevance}
\begin{enumerate}\notsowide
\item \textbf{Appeal to Authority}: Some authority figure concludes that $X$ is true, wrong, etc. Thus $X$ is true, wrong, etc.

\item \textbf{Ad Hominem} (personal attack): Person $Y$ claims $X$ is true. But person $Y$ is a an awful person, a hypocrite, or smells bad. Thus person $Y$'s argument for $X$ can be dismissed.

\item \textbf{Popular Appeal}: Many people endorse $X$, thus $X$ is true, good, etc.

\item \textbf{Appeal to Force}: Believe $X$ or you die!

\item \textbf{Appeal to Consequences}: Theory $X$ has bad consequences, thus theory $X$ is false.

\item \textbf{Naturalistic Fallacy}: $X$ is natural, thus $X$ is good.

\item \textbf{Genetic Fallacy}: $X$ comes from $y$, thus $X$ has all of the features of $y$.

\item \textbf{Red Herring}: You say $X$ is true, good, etc. What about $Y$?

\item \textbf{Weak Analogy}: $X$ has feature $F$. $Y$ is almost, sort of like $X$, so $Y$ has feature $F$. 
\end{enumerate}
\subsubsection*{Fallacies of Ambiguity}
\begin{enumerate}\notsowide
\item \textbf{Equivocation}: One meaning of a word, implies another meaning of the same word.

\item \textbf{Straw Person}: Your argument can be refuted by refuting this much weaker version of it.

\item \textbf{Cherry Picking (Texas Sharpshooter}: These particular data points support $X$, so $X$ is true.


\end{enumerate}

\subsubsection*{Fallacies of Presumption}

\begin{enumerate} \notsowide

\item \textbf{Mere Assertion}: $X$ is true!

\item \textbf{Begging the Question}: $X$ is true, because $X$ is true.

\item \textbf{Appeal to Ignorance}: We are not sure if $X$ is true. So $X$ is false.

\item \textbf{False Dilemma}: Either you accept $X$ or you must accept as the only alternative, awful position $Y$.

\item \textbf{Hasty Generalization}: A small, biased sample shows that $X$ is true.

\item \textbf{Slippery Slope}: If we do innocent-sounding $X$, awful consequence $Y$ will also happen.

\item \textbf{False Cause}: $X$ happened before $Y$, so $X$ caused $Y$.

\item \textbf{Circular Reasoning}: $X$ proves $Y$, and $Y$ proves $X$.
\end{enumerate}





\end{document}
